Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-07-31 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PITT.Rmd
Added markdown to process samples from pitt

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PENN.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PENN')
```

@@

thisFileName <- 'CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_MSSM.Rmd'

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  dplyr::filter(Institution == 'Penn') %>%
  unique

# Replace AFF and BP samples as other
levels(METADATA$Dx) = c("Other", "Other", "Control", "SCZ")
```

@@

  normalizationType	= 'CQN',
  institution = 'PENN'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PENN", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PITT.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PITT')
```

@@

thisFileName <- 'CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PITT.Rmd'

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  dplyr::filter(Institution == 'Pitt', Dx %in% c('Control','SCZ')) %>%
  unique

# Replace AFF and BP samples as other
levels(METADATA$Dx) = c("Control", "SCZ")
```

@@

  normalizationType	= 'CQN',
  institution = 'PITT'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PITT", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
